Towards planning of infantile cardiac surgery based on simulation

### 2012-02-22 Doc/Miccai/miccai2012.tex
more on article
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@326 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

\subsection{shells...}

@@

\section{Method Description}

@@

%\section{Conclusion}
%\subsection{Verification}

@@

% Some Vim setup. If it interferes with anyones work feel free to remove
% that.
% vim: et sw=2 tw=75 fdm=marker spell

>>>>

\subsection{shells...} % {{{

@@

\section{Method Description} % {{{

@@

We propose a different approach which uses a two different mesh topologies.
The basic idea is to transform the mesh by joining the edges and nodes
where the suturing is supposed to take place and let the dynamic system
find a stable configuration. Such stable configuration is the result we are
looking for. This requires us to provide a mapping to the underlying shell
element code that would translate between nodes of the topology of the rest
shape and the topology of the deformed mesh. Such a mapping is 1:N for
nodes where the suturing takes place. \tomas{add image} To make it properly
defined elements have to be taken into account also:

\begin{equation}
  \phi : N_d \times E_d -> N_r
\end{equation}

In the definition of this mapping $\phi$ the $N_d$ and $E_d$ are sets of
nodes and elements of the deformed mesh and $N_r$ is set of nodes of the
deformed mesh.

\tomas{what more?}

Another problem that a predictive simulation should deal with is filling
the missing steps that would normally had to be performed fluently by the
surgeon. For example when suturing two blood vessels together they have to
be placed close to one another first. Sometimes relatively large distances
have to be overcome. By ignoring this fact our approach with joining nodes
and edges could generate unwanted forces at the start of the simulation. To
alleviate large initial deformations for the elements we employed
interpolation ...

\section{Conclusion}
%\subsection{Verification}

@@

% Some Vim setup. If it interferes with anyones work feel free to remove
% that.
% vim: et sw=2 tw=75 fdm=marker fdc=2 spell
